Overlapping Batches for the Assessment of Solution Quality in Stochastic Programs

### 2014-06-27 omrp_lb_rev.tex
variance parameter (Ref2 comment)

\subsection{Overlapping Batch Means} \label{ssec:obm}
Consider a covariance stationary stochastic process with mean $\mu$ and variance $\sigma^2$.  
The task is to estimate $\mu$ given some realization of the univariate stochastic process $\y = (y^1, y^2, \dots, y^n)$.  
Typically, this involves forming a CI of the form $[L_\alpha(\y), U_\alpha(\y)]$ for a given level of significance $\alpha$ such that $\p{L_\alpha(\y) \leq \mu \leq U_\alpha(\y)} = 1 - \alpha$ or that this probability is approximately $1 - \alpha$ for large enough sample sizes.  
The usual estimator for $\mu$ is the sample mean $\ybb = \frac{1}{n} \sum_{i=1}^n y^i$, which is an unbiased estimator even in the presence of correlated data.  
However, the usual variance estimator $\frac{1}{n-1} \sum_{i=1}^n (y^i - \ybb)^2$ can be inappropriate to use in the presence of correlated data, resulting in inaccurate interval estimators.  
To overcome this difficulty, various variance estimators have been proposed in the simulation literature; see, e.g., \citep{law_07}.  
We briefly review two of these variance estimators: nonoverlapping and overlapping batch means.

>>>>

\subsection{Overlapping Batch Means} \label{ssec:obm}
Consider a covariance stationary stochastic process with mean $\mu$ and variance parameter\footnote{For a given process $y^1, y^2, \dots$, the variance parameter is the sum of covariances at all lags, $\sigma^2=\mathrm{Var} \left(y^1 \right)+2\sum_{j=1}^{\infty}\mathrm{Cov} \left(y^1,y^{1+j}\right)$. If the variance parameter exists, then  $\sigma^2=\lim_{n\rightarrow \infty}n\mathrm{Var} \left(\ybb\right)$, where $\ybb=\frac{1}{n}\sum_{i=1}^{n} y^{i}$.} $0<\sigma^2<\infty$.  
The task is to estimate $\mu$ given some realization of the univariate stochastic process $\y = (y^1, y^2, \dots, y^n)$.  
Typically, this involves forming a CI of the form $[L_\alpha(\y), U_\alpha(\y)]$ for a given level of significance $\alpha$ such that $\p{L_\alpha(\y) \leq \mu \leq U_\alpha(\y)} = 1 - \alpha$ or that this probability is approximately $1 - \alpha$ for large enough sample sizes.  
The usual estimator for $\mu$ is the sample mean $\ybb = \frac{1}{n} \sum_{i=1}^n y^i$, which is an unbiased estimator even in the presence of correlated data.  
However, the usual variance estimator $\frac{1}{n-1} \sum_{i=1}^n (y^i - \ybb)^2$ can be inappropriate to use in the presence of correlated data, resulting in inaccurate interval estimators.  
To overcome this difficulty, various variance estimators have been proposed in the simulation literature; see, e.g., \citep{law_07}.  
We briefly review two of these variance estimators: nonoverlapping and overlapping batch means.
